### 2020-04-08 probabilisticProgrammingMartingales.tex
minor

    \lo{For the integral to be well-defined, we need $x \mapsto E[\underline x]$ to be a measurable function $\mathbb{R} \to \mathit{Rch}(M)$.}

>>>>

    \lo{For the integral to be well-defined, we need $x \mapsto E[\underline x]$ to be a measurable function $\mathbb{R} \to \mathit{Rch}(M)$ (I am sure it is, assuming an appropriate definition of SPCF terms as a measurable space.).}
